Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-15 paper/paper.tex
Grammar issue

In this section we show that the classic \emph{rent-or-buy} approach\cite{borodin-book}\maciek{any better source? ski rental?} allows to obtain an optimal algorithm for $k=3$.
Upon receiving $\alpha$ requests between a pair of nodes, we collocate them in one server until the end of an epoch (that we define precisely later).
To this end, we maintain \emph{components of nodes}, in similar fashion to previous approaches\cite{repartition-disc}.

@@

We define the algorithm \TAlg in the following way.
\TAlg partition nodes into components.
Intially, each node is in its own singleton component.
For each pair of nodes \TAlg maintains a counter, initiated $0$. 
Upon receiving a request to a pair that is not collocated at one server, it increases the counter by $1$.
If the counter for a pair $(u,v)$ reaches $\alpha$, \TAlg merges the components of $u$ and $v$, and moves to the closest partition, in which each component has all of its nodes collocated in one server.
If no such partition exists, \TAlg resets all components to singletons and all counters to $0$ and ends the phase.

>>>>

In this section we show that the classic \emph{rent-or-buy} approach\cite{borodin-book}\maciek{any better source? ski rental?} allows to obtain an optimal algorithm for $k=3$.
Upon receiving $\alpha$ requests between a pair of nodes, we collocate them in one server until the end of an epoch (that we define precisely later).
To this end, we maintain \emph{components of nodes}, in the similar fashion to previous approaches\cite{repartition-disc}.

@@

%We define the algorithm \TAlg in the following way.
Now we describe the algorithm \TAlg.
\TAlg partition nodes into components, and
intially each node belongs to its own singleton component.
For each pair of nodes \TAlg maintains a counter, initiated to $0$. 
Upon receiving a request to a pair that is not collocated at one server, it increases the counter by $1$.
If the counter for a pair $(u,v)$ reaches $\alpha$, \TAlg merges the components of $u$ and $v$, and moves to the closest partition, in which each component has all of its nodes collocated in one server.
If no such partition exists, \TAlg resets all components to singletons and all counters to $0$ and ends the phase.
